Notes on ``A nonlocal anisotropic model for phase transitions (Alberti 97)''

### 2021-12-23 references/notes/alberti97.tex

%%% Distribution related notation
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ebb}{\mathbb{E}}
% \newcommand{\Pr}{\mathrm{Pr}}}

@@

%%% Functionals over graphs
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\vol}{\mathrm{vol}}
% \newcommand{\deg}{\mathrm{deg}}

@@

\title{Notes for the week of 4/8/19 - 4/12/19}
\author{Alden Green}
\date{\today}
\maketitle

Let $\set{x_1, x_2, \ldots}$ be a sequence of points sampled independently from probability measure $\Pbb$ with density function $f$. For each $n$, write $\Xbf_n = \set{x_1, \ldots, x_n} \subseteq \Reals^d$ . Given some $\lambda, \sigma > 0$, let
\begin{equation*}
\mathcal{U} = \set{x: f(x) \geq \lambda},~ \mathcal{C} = \textrm{one connected component of}~ \mathcal{U}, ~\textrm{and}~ \Csig = \Cset + B(0,\sigma)
\end{equation*}

Write $\widetilde{\Xbf}_n = \Csig[\Xbf_n]$, $\widetilde{E}_n = \set{(i,j): x_i, x_j \in \widetilde{\Xbf}_n, \norm{x_i - x_j}_2 \leq r}$ and let $\widetilde{G}_{n,r} = \bigl(\widetilde{\Xbf}_n, \widetilde{E}_n \bigr)$.
For a set $S \subseteq \widetilde{\Xbf}_n$, the normalized cut of $S$ within $\widetilde{G}_{n,r}$ can be defined as
\begin{equation*}
\widetilde{\Phi}_{n,r}(S) := \frac{\widetilde{\cut}(S)}{\min \set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}},~ \textrm{where}~ \widetilde{\cut}(S) := \cut(S;\widetilde{G}_{n,r}),~ \widetilde{\vol}(S) := \vol(S;\widetilde{G}_{n,r})
\end{equation*}
and in this context $S^c = \widetilde{\Xbf}_n \setminus S$ denotes the complement of $S$ within $\widetilde{G}_{n,r}$. Then, the \emph{graph conductance profile} over $\widetilde{G}_{n,r}$ is
\begin{equation*}
\widetilde{\Phi}_{n,r}(t) := \min_{\substack{S \subseteq \widetilde{\Xbf}_n: \\ 0 < \widetilde{\pi}_n(S) < t} } \widetilde{\Phi}_{n,r}(S)
\end{equation*}
where $\widetilde{\pi}_{n,r}(S) = \frac{\widetilde{\vol}(S)}{\widetilde{\vol}(\widetilde{\Xbf}_n)}$. We will prove a lower bound on the graph conductance profile by a continuous analogue.

\subsection{Continuous conductance}

Let $\nu$ be the Lebesgue measure over Euclidean space $\Rd$, and $B(x,r)$ be a ball of radius $r$ centered at $x$. For $\Sset \subset \Rd$ a Borel set,
\begin{equation*}
\nu_{\Pbb}(\Sset) := \int_{\Sset} f(x) dx
\end{equation*}
is the weighted volume.

The $r$-ball walk over $\Csig$ is a Markov chain, with transition probability given by 
\begin{equation*}
\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\nu_{\Pbb}(\Sset \cap B(x,r))}{\nu_{\Pbb}(\Csig \cap B(x,r))} \tag{$x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
where $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.

Denote the stationary distribution for this Markov chain by $\pi_{\Pbb,r}$, which is defined by the relation
\begin{equation*}
\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\pi_{\Pbb,r}(x) = \pi_{\Pbb,r}(\Sset).  \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
Letting the \emph{local conductance} be given by
\begin{equation*}
\ell_{\Pbb,r}(x) := \nu_{\Pbb}(\Csig \cap B(x,r)) \tag{$x \in \Csig$}
\end{equation*}
a bit of algebra verifies that
\begin{equation*}
\pi_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) dx}. \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}

We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
\begin{equation*}
\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\pi_{\Pbb,r}(x), \tag{$\Sset_1, \Sset_2 \in \mathfrak{B}(\Csig)$}
\end{equation*}
the \emph{(continuous) normalized cut} by
\begin{equation*}
\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2)}{\min \set{\pi_{\Pbb,r}(\Sset),\pi_{\Pbb,r}(\Sset^c)}}, \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
and the \emph{(continuous) conductance profile} by
\begin{equation*}
\widetilde{\Phi}_{\nu,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \pi_{\Pbb,r}(\Sset) \leq t} } \widetilde{\Phi}_{\Pbb,r}(\Sset) \tag{$0 < t \leq 1/2 $}
\end{equation*}
where $\Sset^c = \Csig \setminus \Sset$.

To relate the graph and continuous conductance profiles, we introduce mappings between the data $\widetilde{\Xbf}_n$ and the space $\Csig$.

\subsection{Transportation maps and $TL^1$ distance. }
Let
\begin{equation*}
\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\widetilde{n}} \sum_{x_i \in \widetilde{\Xbf}_n} \1(x_i \in \Sset) \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*} 
be the (empirical) probability measures, conditional on $x \sim \Pbb$ lying within $\Csig$ (Here $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$). A Borel map $T: \Csig \to \widetilde{\Xbf}_n$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for arbitrary $\Sset \in \mathfrak{B}(\Csig)$,  
\begin{equation*}
\widetilde{\Pbb}(\Sset) = \widetilde{\Pbb}_n(T(\Sset)).
\end{equation*}

If a sequence of transportation maps $\seq{T_n}$ satisfies $\norm{\mathrm{Id} - T_n}_{L^{1}(\widetilde{\Pbb})} = o_P(1)$, we refer to it as a sequence of \emph{stagnating transportation maps}. Lemma \ref{lem: stagnating_transportation_maps} establishes that with probability one, such a sequence of stagnating transportation maps will exist.
In fact, under suitable conditions, the convergence happens at rate $\left(\frac{\log n}{n}\right)^{1/d}$.

\begin{lemma}[Adaptation of Proposition 5 of \textcolor{red}{Garcia Trillos 2016}]
	\label{lem: stagnating_transportation_maps}
	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \widetilde{\Xbf}_n$ such that the following statement holds:
	\begin{equation*}
	\limsup_{n \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq C
	\end{equation*}
	where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$, $C$ is a universal constant and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
\end{lemma}

\begin{definition}
	For a sequence $\seq{u_n} \subseteq L^1(\widetilde{\Pbb}_n)$ and $u \in L^1(\widetilde{\Pbb})$, we say that $\seq{u_n}$ converges $TL^1$ to $u$ if there exists a sequence of stagnating transportation maps $\seq{T_n}$ such that
	\begin{equation}
	\label{eqn: transportation_distance_1}
	d^{TL^1}(u,u_n) := \int_{\Csig} \abs{u(x) - u_n \circ T_n(x)} d \widetilde{\Pbb}(x) \overset{n}{\to} 0 
	\end{equation}
	and denote it $u_n \overset{TL^1}{\to} u$.
\end{definition}

\begin{remark}
	\label{rmk: transportation_distance_equivalence}
	Note that as written this is not a metric, as $u$ and $u_n$ lie in different spaces. Technically, we can resolve this by writing
	\begin{equation}
	\label{eqn: transportation_distance_2}
	d^{TL^1}((\widetilde{\Pbb}, u),(\widetilde{\Pbb}_n,u_n)) = \inf_{\pi \in \Gamma(\widetilde{\Pbb},\widetilde{\Pbb}_n)} \iint_{\Csig \times \Csig} \abs{x - y} + \abs{f(x) - g(y)} d\pi(x,y)
	\end{equation}
	where $\gamma$ is the space of couplings over the measures $\widetilde{\Pbb}, \widetilde{\Pbb}_n$. However, it can be shown that \eqref{eqn: transportation_distance_2} converges to zero if and only if \eqref{eqn: transportation_distance_1} is satisfied and 
	\begin{equation*}
	\widetilde{\Pbb}_n \overset{w}{\to} \widetilde{\Pbb}.
	\end{equation*}

	Since this additional condition will be satisfied with probability one, we simplify things by hereafter referring only to the condition in \eqref{eqn: transportation_distance_1}. See \textcolor{red}{Garcia Trillos 15} for more details.
\end{remark}

\section{Lower bound graph conductance profile}

In order to lower bound the graph conductance profile $\widetilde{\Phi}_{n,r}(\cdot)$, we will need to split the analysis into two cases based on the size of $S \subseteq \widetilde{\Xbf}_n$. Define the \emph{graph local spread} to be
\begin{equation*}
s(G) := \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)} \cdot \min_{u \in V} \set{\pi(u;G)}.  \tag{$G = (V,E)$}
\end{equation*}

Theorem \ref{thm: graph_conductance_profile_lb_1} states that for subsets of $\widetilde{\Xbf}_n$ with volume at least $s(G)$, the graph normalized cut can be uniformly lower bounded by the continuous normalized cut. Sections \ref{sec: proof_and_supporting_theory} and \ref{sec: other_results} contains the proof of Theorem \ref{thm: graph_conductance_profile_lb_1} along with other relevant results.

\begin{theorem}
	\label{thm: graph_conductance_profile_lb_1}
	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} with respect to Lipschitz constant $L$ and convex set $K$ with diameter $D_K$. Then,
	\begin{equation*}
	\liminf_{n \to \infty} \Bigl\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \Bigr\} \geq \frac{\lambda_{\sigma}^4 r}{\Lambda_{\sigma}^4 2^{12} D_K L \sqrt{d}}
	\end{equation*}
	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \widetilde{\Xbf}_n: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$
\end{theorem}

Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for the remaining small sets, the graph normalized cut is of constant order. 
\begin{lemma}
	\label{lem: graph_conductance_profile_lb_1}
	Let $G = (V,E)$ be an undirected graph, and $\mathcal{L}(G) = \set{S \subseteq V: \pi(S; G) \geq s(G)}$. Then,
	\begin{equation*}
	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
	\end{equation*}
\end{lemma}
\begin{proof}
	Clearly, for any $u \in S$
	\begin{equation}
	\label{eqn: graph_conductance_profile_lb_1}
	\cut(\set{u}, S^c; G) \geq \deg(u;G) - \abs{S}
	\end{equation}

	Then, since $\pi(S;G) \leq s(G)$,
	\begin{equation*}
	\abs{S} \leq \pi(S;G) \cdot \frac{\vol(V;G)}{\min_{u \in V} \set{\mathrm{deg}(u;G)}} = \frac{\pi(S;G)}{\min_{u \in V} \set{\pi(u;G)}} \leq \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)},
	\end{equation*}
	and therefore by \eqref{eqn: graph_conductance_profile_lb_1}, for any $u \in S$
	\begin{equation*}
	\cut(\set{u}, S^c; G) \geq \deg(u;G) - \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)} \geq \frac{1}{10}\deg(u;G)
	\end{equation*}
	and the statement follows by summing over all $u \in S$. 
\end{proof}

Theorem \ref{thm: graph_conductance_profile_lb_1} and Lemma \ref{lem: graph_conductance_profile_lb_1} together yield Corollary \ref{cor: graph_conductance_profile_lb}, the main result of these notes.

\begin{corollary}[Lower bound on graph conductance profile]
	\label{cor: graph_conductance_profile_lb}
	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} with respect to Lipschitz constant $L$ and convex set $K$ with diameter $D_K$. Then, with probability one the following asymptotic lower bound holds on the graph conductance function
	\begin{equation*}
	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \min\set{\frac{\lambda_{\sigma}^4 r}{\Lambda_{\sigma}^4 2^{12} D_K L \sqrt{d}}, \frac{1}{10}} \tag{$0 \leq t \leq \frac{1}{2}$}
	\end{equation*}
\end{corollary}

\section{Proofs and Supporting Theory}
\label{sec: proof_and_supporting_theory}

\subsection{Proof of Theorem \ref{thm: graph_conductance_profile_lb_1}.}

By Lemma \ref{lem: stagnating_transportation_maps}, with probability one there exists a sequence of stagnating transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, which we will denote $\seq{T_n}$.

For $S \subseteq \widetilde{\Xbf}_n$, let $T_n^{-1}(S) = \set{x \in \Csig: T_n(x) \in S}$ be the preimage of $T_n$, and note that $T_n^{-1}(S^c) = \Csig \setminus T_n^{-1}(S)$.

Letting
\begin{equation*}
\xi_n := \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx},~ \gamma_n(S) := \frac{\min \set{\pi_{\Pbb,r_n^-}(T_n^{-1}(S^c)), \pi_{\Pbb,r_n^-}(T_n^{-1}(S^c))} }{\min \set{\pi_{\Pbb,r_n^+}(T_n^{-1}(S^c)), \pi_{\Pbb,r_n^+}(T_n^{-1}(S^c))} } 
\end{equation*}
where $r_n^{\pm} := r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, by Lemma \ref{lem: graph_to_continuous_conductance} and Corollary \ref{cor: nonuniform_continuous_conductance} we have that for all $S \subseteq \widetilde{\Xbf}_n$,
\begin{align}
\widetilde{\Phi}_{n,r}(S) & \geq \xi_n \gamma_n(S) \widetilde{\Phi}_{\Pbb,r_n^{-}}(T_n^{-1}(S)) \nonumber \\
& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^4r_n^{-}}{2^{12} \Lambda_{\sigma}^4 D_K L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
\end{align}

By Lemma \ref{lem: cont_local_conductance}, with probability one
\begin{equation*}
\liminf_{n \to \infty} \xi_n = 1.
\end{equation*}

By Lemma \ref{lem: stationary_dist_lb}, letting $c$ be any constant satisfying $c > \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2}$, there exists some $n \in \Naturals$ such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
\begin{equation*}
\pi_{\Pbb,r}(T_n^{-1}(S)) \geq c > 0
\end{equation*}
and therefore by Lemma \ref{lem: cont_stationary_dist}
\begin{equation*}
\liminf_{n \to \infty} \biggl\{ \inf_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \gamma_n(S)\biggr\} = 1.
\end{equation*}

As Lemma \ref{lem: stagnating_transportation_maps} implies $r_n^{-} \to r$ with probability one, an application of Slutsky's Theorem to \eqref{eqn: graph_ncut_lb_1} completes the proof.

\subsection{Graph functionals to continuous functionals.}

Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} provide the necessary bounds for the $\cut$ and $\vol$ functionals in terms of continuous analogues.

\begin{lemma}
	\label{lem: volume_bound}
	Let $S \subseteq \widetilde{\Xbf}_n$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$
	\begin{equation*}
	\frac{1}{\widetilde{n}^2}\widetilde{\vol}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\Pbb(\Csig)^2} \pi_{\Pbb,r_n^+}(\Sset)
	\end{equation*}
	where $r_n^+ = r + \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$. 
\end{lemma}
\begin{proof}
	Let $u: \widetilde{\Xbf}_n \to \set{0,1}$ be the characteristic function for $S$, meaning
	\begin{equation*}
	u(x) = 
	\begin{cases}
	1,~ x \in S \\
	0,~ \text{otherwise}
	\end{cases}
	\end{equation*}

	Now, we proceed
	\begin{align}
	\frac{1}{\widetilde{n}^2} \widetilde{\vol}(S_n) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \widetilde{\Xbf}_n} \1(\norm{x_i - x_j} \leq r) \abs{u(x_i)} \nonumber \\
	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{u(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{u \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
	& \leq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{u \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \label{eqn: vol_ub}\\
	& = \int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
	\end{align}

	By definition we have $\frac{d\widetilde{\Pbb}(x)}{d\Pbb(x)} = \Pbb(\Csig)$. Therefore,
	\begin{align*}
	\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\Pbb(y) d\Pbb(x) \\
	& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r_n^+}(x) f(x) dx \\
	& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) dx}{\Pbb(\Csig)^2} \pi_{\Pbb,r_n^+}(\Sset)
	\end{align*}
	which is the desired upper bound. The lower bound follows a similar proof, with the only change being \eqref{eqn: vol_ub}, where $r_n^+$ is replaced by $r_n^-$ and the inequality is reversed.
\end{proof}

\begin{lemma}
	\label{lem: cut_bound}
	Let $S \subseteq \widetilde{\Xbf}_n$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$,
	\begin{equation*}
	\frac{1}{\widetilde{n}^2} \widetilde{\cut}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c) 
	\end{equation*}
	where $r_n^- = r - \norm{\mathrm{Id} - T_n}_{L^\infty(\widetilde{\Pbb})}$
\end{lemma}
\begin{proof}
	Let $u: \widetilde{\Xbf}_n \to \set{0,1}$ be the characteristic function for $S$, meaning
	\begin{equation*}
	u(x) = 
	\begin{cases}
	1,~ x \in S \\
	0,~ \text{otherwise}
	\end{cases}
	\end{equation*}

	We proceed according to a very similar set of steps as Lemma \ref{lem: volume_bound}:
	\begin{align*}
	\frac{1}{\widetilde{n}^2} \widetilde{\cut}(S) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \widetilde{\Xbf}_n} \1(\norm{x_i - x_j} \leq r) \abs{u(x_i) - u(x_j)} \\
	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{u(x) - u(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{u \circ T_n(x) - u \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
	& \geq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{u \circ T_n(x) - u \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
	& = \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
	\end{align*}
	We conclude similarly to the proof of Lemma \ref{lem: volume_bound},
	\begin{align*}
	\int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\Pbb(y) d\Pbb(x) \\
	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
	\end{align*}	
\end{proof}

\begin{lemma}
	\label{lem: graph_to_continuous_conductance}
	Let $\seq{T_n}$ be a sequence of transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, and let
	\begin{equation*}
	r_n^- = r - \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})},~ r_n^+ = r + \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}.
	\end{equation*}

	Fix $S \subseteq \widetilde{\Xbf}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$,
	\begin{equation}
	\label{eqn: graph_to_continuous_conductance}
	\widetilde{\Phi}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}  \frac{\min \set{\pi_{\Pbb,r_n^-}(\Sset), \pi_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} } \widetilde{\Phi}_{\Pbb,r_n^{-}}(\Sset)
	\end{equation}
\end{lemma}
\begin{proof}

	By Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound},
	\begin{equation*}
	\frac{\widetilde{\cut}(S)}{\widetilde{\vol}(S)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\pi_{\Pbb,r_n^+}(\Sset)}
	\end{equation*}

>>>>

%%% Distribution related notation
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
% \newcommand{\Pr}{\mathrm{Pr}}}

@@

%%% Functions over graphs
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\vol}{\mathrm{vol}}

@@

\title{Notes on ``A nonlocal anisotropic model for phase transitions (Alberti 97)''}
\author{Alden Green}
\date{\today}
\maketitle

Let $\Csig = \Cset + B(0,\sigma)$ for some $\Cset \subset \Reals^d$. Define the nonlocal functional $F_{r}(v, \Csig)$ to be
\begin{equation*}
F_r(v, \Csig) := \frac{1}{4r} \iint_{\Csig} \frac{\1(\norm{x - y} \leq r)}{r^d} (v(x) - v(y))^2 dx dy + \frac{1}{r} \int_{\Csig} W(v(x)) dx
\end{equation*}
where $W:\Reals \to \Reals$ is a continuous function which vanishes at $\pm 1$ only and has at least \textcolor{red}{linear growth at infinity}.

\begin{theorem}[Theorem 3.1]
	Let $r_n \to 0$, $v_{n}: \Csig \to [-1,1]$ be such that $F_{r_n}(v_n, \Csig)$ is bounded. Then the sequence $\seq{v_n}$ is precompact in $L^1(\Csig)$. 
\end{theorem}
\begin{proof}
	Throughout, let  $J_r(\norm{x - y}) := \frac{\1(\norm{x - y} \leq r)}{r^d}$. 
	\item

	\textbf{Step 1:} At first, we will assume each $v_n$ takes values in $\pm1$ only.

	Extend each function $v_n$ to $1$ in $\Reals^d \setminus \Csig$, and observe that our hypothesis implies (\textcolor{red}{omitting the proof})
	\begin{equation}
	\label{eqn: nonlocal_functional_bound}
	\iint_{\Reals^d \times \Reals^d} J_r(\norm{x - y}) \abs{v_n(x) - v_n(y)} dy dx = \mathcal{O}(r)
	\end{equation} 
	Moreover, it is an easily verifiable fact that for every non-negative $g \in L^1(\Reals^d)$,
	\begin{equation*}
	\iint_{\Reals^d \times \Reals^d} (g \ast g)(x - y) \abs{u(x) - u(y)} dy dx \leq 2 \norm{g}_1 \iint_{\Reals^d \times \Reals^d} g(x - y) \abs{u(x) - u(y)} dx dy
	\end{equation*}
	and in combination with \eqref{eqn: nonlocal_functional_bound} this implies
	\begin{equation}
	\label{eqn: nonlocal_functional_bound_1}
	\iint_{\Reals^d \times \Reals^d} (J_r \ast J_r)(x - y) \abs{u(x) - u(y)} dy dx = \mathcal{O}(r)
	\end{equation}

	Since $J \ast J$ is a nonnegative continuous function, we may find a nonnegative smooth function $\varphi$ with compact support such that
	\begin{equation}
	\label{eqn: varphi}
	\varphi \leq J_r \ast J_r,~ \abs{\nabla \varphi} \leq J \ast J.
	\end{equation}
	Letting $c = \int_{\Reals^d} \varphi(y) dy$, for $y \in \Reals^d$ define
	\begin{equation*}
	\varphi_r(y) := \frac{1}{cr^d} \varphi\left(\frac{y}{r}\right),~ w_n(y) := \varphi_{r_n} \ast v_n(y)
	\end{equation*}
	We claim that $\seq{w_n}$ is asymptotically equivalent to $\seq{v_n}$ in $L^1(\Reals^d)$ and that the gradients $\nabla{w_n}$ are uniformly bounded in $L^1(\Reals^d)$. Suppose this were true; then by Theorem \ref{thm: poincare}
	\begin{equation*}
	\norm{w_n}_{L^1(\Csig)} \leq \norm{w_n}_{L^{p^{\star}}(\Csig)} \leq \norm{w_n}_{L^{p*}(\Reals^d)} \leq C \norm{\nabla w_n}_{L^1(\Reals^d)} < \infty
	\end{equation*}
	and so $w_n \in W_{1,1}(\Csig)$. By the Rellich-Kondrachov Compactness Theorem (Theorem \ref{thm: arzela_ascoli}), $\seq{w_n}$ is precompact in $L^1(\Csig)$.

	It remains to prove the claim. We have
	\begin{align*}
	\int_{\Reals^d} \abs{w_n(x) - v_n(x)} dx & = \int_{\Reals^d} \abs{ \int_{\Reals^d} \varphi_{r_n}(v_n(y) - v_n(x)) dy} dx \\
	& \leq \iint_{\Reals^d \times \Reals^d} \abs{\varphi_{r_n}(\norm{x - y})} \abs{v_n(y) - v_n(x)} dy dx \\
	& \leq \frac{1}{c} \iint_{\Reals^d \times \Reals^d} (J \ast J)(\norm{x - y}) \abs{v_n(y) - v_n(x)} dy dx = \mathcal{O}(r).
	\end{align*}
	where the last equality follows from \eqref{eqn: nonlocal_functional_bound_1}.

	Moreover, 
	\begin{align*}
	\int_{\Reals^d} \abs{\nabla w_n} dx & = \int_{\Reals^d} \abs{\int_{\Reals^d} \nabla \varphi_{r_n}(x - y) u_n(y) dy} dx \\
	& \overset{(i)}{=} \int_{\Reals^d} \abs{\int_{\Reals^d} \nabla \varphi_{r_n}(x - y) (u_n(y) - u_n(x)) dy} dx \\
	& \leq \iint_{\Reals^d \times \Reals^d} \abs{\nabla \varphi_{r_n}(x - y)} (u_n(y) - u_n(x)) dy dx \\
	& \overset{(ii)}{\leq} \frac{1}{cr}  \iint_{\Reals^d \times \Reals^d} (J_r \ast J_r)(x-y) (u_n(y) - u_n(x)) dy dx \\
	& \overset{(iii)}{=} \mathcal{O}(1),
	\end{align*}
	where $(i)$ follows from $\int_{\Reals^d} \nabla \varphi_{r_n}(x - y) dy = 0$, in the light of the fact that $\varphi$ has compact support; $(ii)$ follows from \eqref{eqn: varphi}; and $(iii)$ from \eqref{eqn: nonlocal_functional_bound_1}.
\end{proof}

\section{Additional Information}

For a function $J$, we write $J_r(x) := \frac{1}{r^d} J\left(\frac{x}{r}\right)$.

The mollification of a function $f:\Reals^d \to \Reals$ by a mollifier $J_{r}$ is written $f_r: \Reals^d \to \Reals$, and is given by
\begin{equation*}
f_r(x) := J_r \ast f = \int_{\Reals^d} J_r(x - y) f(y) dy.
\end{equation*}

\begin{theorem}[Arzela-Ascoli]
	\label{thm: arzela_ascoli}
	Suppose $\seq{f_n}$ is a sequence of real-valued functions defined on $\Reals^d$ such that for all $k \in \Naturals$, $x \in \Reals^d$,
	\begin{equation*}
	\abs{f_n(x)} \leq M
	\end{equation*}
	for some constant $M$, and that moreover the functions $f_n$ are \emph{uniformly equicontinuous}, meaning that for each $\epsilon > 0$ there exists $\delta > 0$ such that 
	\begin{equation*}
	\abs{x - y} < \delta~ \Longrightarrow~ \abs{f_n(x) - f(n)}. \tag{for all $x,y \in \Reals^d$}
	\end{equation*}

	Then, there exists a subsequence $(f_{n_k})_{k \in \Naturals}$ and a continuous function $f$ such that
	\begin{equation*}
	f_{n_k} \to f~~ \textrm{uniformly on compact subsets of}~ \Reals^d
	\end{equation*}
\end{theorem}

\begin{definition}
	Let $X$ and $Y$ be Banach spaces, $X \subset Y$. We say that $X$ is \emph{compactly embedded} in $Y$, written
	\begin{equation*}
	X \subset \subset Y
	\end{equation*}
	if 
	\begin{enumerate}[(i)]
		\item $\norm{u}_Y \leq C \norm{u}_X$ for some constant $C$, and
		\item each bounded sequence in $X$ is precompact in $Y$. 
	\end{enumerate}
\end{definition}

Recall that the Sobolev conjugate is $p^*= \frac{pn}{n - p}$.

\begin{theorem}[Rellich-Kondrachov Compactness Theorem]
	\label{thm: compact_embedding}
	Assume $U$ is a bounded open subset of $\Reals^d$ and $\partial U$ is $C^1$. Suppose $1 \leq p < d$. Then
	\begin{equation*}
	W^{1,p}(U) \subset \subset L^q(U)
	\end{equation*}
	for $1 \leq q < p^{\star}$. In particular, since $p^{*} > p$, we have
	\begin{equation*}
	W^{1,p}(U) \subset \subset L^p(U)
	\end{equation*}
	for all $1 \leq p$.
\end{theorem}

\begin{theorem}[Gagliardo-Nirenberg-Sobolev]
	\label{thm: poincare}
	Assume $1 \leq p < d$. There exists constant $C$, depending only on $p$ and $d$, such that
	\begin{equation*}
	\norm{u}_{L^{p^*}(\Reals^d)} \leq C \norm{D u}_{L^{p}(\Reals)}
	\end{equation*}
	for all $u \in C_c^1(\Reals^d)$. 
\end{theorem}
\end{document}
